30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-12 paper.tex
fixed merge conflicts from master

		\subsection{Bootstrapping}

@@

@@

	\section{Comparison existing decentralized  networks}

>>>>

			\subsection{Bootstrapping new nodes}
		If a Tor user decides to donate some of his bandwidth by running a bridge or a relay and thus creating a new node in the network, there has to be one starting point where this new node can discover neighbors in the network to connect with. In Tor a directory server can tell the new node what his neighbors are and how to find them \cite{dingledine2004tor}.
Moving this system to a non peer-to-peer base is difficult. Dingledine et al. stated that this indeed is still an open problem. With decentralized systems there is no central directory server to tell a new node where to locate neighbors and there might be a lot of malicious nodes in the network. Some systems such as Tarzan, MorphMix and Pastra [citjes hiero] do have made some attempts towards a decentralized system, but have yet to find the final answer.

		\subsection{Incentives in decentralized systems}

@@

	\section{Comparison existing decentralized  networks}
Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers]. Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here. Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]

@@
